---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PlatFormDesignTimeTrend

<!-- badges: start -->
<!-- badges: end -->

The goal of PlatFormDesignTimeTrend is to simulates the multi-arm multi-stage or platform trial with Bayesian approach using the 'rstan' package, which provides the R interface for to the stan. The package uses Thall's and Trippa's randomisation approach for Bayesian adaptive randomisation. In addition, the time trend problem of platform trial can be studied in this package. There is a demo for multi-arm multi-stage trial for two different null scenario in this package.

## Installation

You can install the 'PlatFormDesignTimeTrend' package 1.0.0 like so:

``` {r}
# install.packages("PlatFormDesignTimeTrend")
devtools::install_github("ZXW834/PlatFormDesignTime", build_vignettes = TRUE)
```

## Demo
- `Demo_CutoffScreening()` is a demo function performing cutoff screening process
- `Demo_multiplescrenariotrialsimulation()` is a demo function performing MAMS trial simulation 

## Tutorials
- `MAMS-CutoffScreening-tutorial` is a tutorial document of how to do cutoff screening under Bayesian MAMS trial
- `MAMS-trial-simulation-tutorial` is a tutorial document of how to do Bayesian MAMS trial simulation with or without time trend 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PlatFormDesignTimeTrend)
## basic example code
Trial.simulation (ntrials = 10,
trial.fun = simulatetrial,
 input.info = list(
   response.probs = c(0.4, 0.4),
   ns = c(30, 60, 90, 120, 150),
   max.ar = 0.75,
   rand.type = "Urn",
   max.deviation = 3,
   model.inf = list(
     model = "tlr",
     ibb.inf = list(
       pi.star = 0.5,
       pess = 2,
       betabinomialmodel = ibetabinomial.post
     ),
     tlr.inf = list(
       beta0_prior_mu = 0,
       beta1_prior_mu = 0,
       beta0_prior_sigma = 2.5,
       beta1_prior_sigma = 2.5,
       beta0_df = 7,
       beta1_df = 7,
       reg.inf =  "main",
       variable.inf = "Fixeffect"
     )
   ),
   Stopbound.inf = Stopboundinf(
     Stop.type = "Early-Pocock",
       Boundary.type = "Symmetric",
         cutoff = c(0.99, 0.01)
         ),
   Random.inf = list(
     Fixratio = FALSE,
     Fixratiocontrol = NA,
     BARmethod = "Thall",
     Thall.tuning.inf = list(tuningparameter = "Fixed",  fixvalue = 1)
   ),
   trend.inf = list(
     trend.type = "step",
     trend.effect = c(0, 0),
     trend_add_or_multip = "mult"
   )
 ),
 cl = 2)
```

